<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-12-08 MainAnalysis.Rmd
Adding new plotting function

```{r, run_invivoPKfit_1comp, eval = FALSE}

devtools::load_all("invivopkfit")

### do 1-Compartment fit
system.time(
  capture.output(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_1comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

```{r, run_invivoPKfit_2comp, eval = FALSE}
devtools::load_all("invivopkfit")

### do 2-Compartment fit
system.time(
  capture.output(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_2comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat, eval = FALSE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))

write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```

```{r, read_data}

### this block reads the exported model fit csv files from run_invivoPKfit

pk_output_2comp <- read.csv(paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""))
pk_output_flat <- read.csv(paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""))
pk_output_1comp <- read.csv(paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""))

raw_1comp <- read.csv(paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""))
raw_2comp <- read.csv(paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""))
raw_flat <- read.csv(paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""))

pk_output_2comp$Vdist <- pk_output_2comp$V1*(pk_output_2comp$k12+pk_output_2comp$k21)/pk_output_2comp$k21

@@

>>>>

```{r, run_invivoPKfit_1comp}

run_timestamp_1comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = TRUE
  )
)

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    run_timestamp_1comp,
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

```{r, run_invivoPKfit_2comp}

run_timestamp_2comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

### do 2-Compartment fit
system.time(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = TRUE
    )
)

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    run_timestamp_2comp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat}
run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

system.time(
    PK.fit.table.flat <- fit_all(
      data.set = cvt.data,
      model = "flat",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = TRUE
    )
)

write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
                                    run_timestamp_flat,
                                    ".csv",
                                    sep=""), row.names = FALSE)
```

For ease of plotting, get the pre-processed, harmonized data:

```{r}
DF <- preprocess_data(data.set = cvt.data,
                       ratio.data.to.dose = 1,
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,)
```

```{r, read_data, eval = FALSE}
### this block reads the exported model fit csv files from run_invivoPKfit

pk_output_2comp <- read.csv(paste("inst/ext/PK_fit_table_2comp_",run_timestamp_1comp,".csv",sep=""))
pk_output_flat <- read.csv(paste("inst/ext/PK_fit_table_flat.",run_timestamp_2comp,".csv",sep=""))
pk_output_1comp <- read.csv(paste("inst/ext/PK_fit_table_1comp_",run_timestamp_flat,".csv",sep=""))

@@

Rowbind together all of the fitted parameter tables into one big one.
```{r}
pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
                         "2comp" = PK.fit.table.2comp,
                         "flat" = PK.fit.table.flat),
                    idcol = "Model",
                    use.names = TRUE,
                    fill = TRUE)
```

Get a table of the winning model for each dataset (minimum AIC).

```{r}
setorder(pk_fit,
         Analysis_Type,
         DTXSID,
         Species,
         AIC,
         na.last = TRUE)

pk_fit_win <- unique(pk_fit[, .(Analysis_Type, DTXSID, Species, model, AIC)] )
```

Plot concentration vs time with the best-fit params by data subset (DTXSID and species).

Indicate the following:

- One line for each model
- Which is the winning model
- Dose group
- Blood vs. plasma
- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
- IV vs. oral administration

Would also like to plot uncertainty in predictions based on uncertainty in parameter estimates.

Plot versions:
- Winning model only
- One model at a time
- All three models on same plot

```{r}

plot_table <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, Reference)])
plot_table <- plot_table[Analysis_Type %in% "Joint"]

tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
                     Analysis_Type_in = plot_table$Analysis_Type,
                     Reference_in = plot_table$Reference,
              MoreArgs = list(
                     model_in = c("1compartment", "2compartment", "flat"),
                     fitdata = DF,
                     pk_fit = pk_fit)
                     )
    ```
